Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2024-03-30 2_SSL_NE/article/article_main.tex
edits in supplement

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=\textwidth]{figures/history_efficacy.pdf}
 \caption{\textbf{Historical progress in the luminous efficacy ($\eta$) of the most widely-used lighting technologies in human history.} Data points indicate best performers by year of market introduction. Luminous efficacy is the measure of how efficiently a light source converts electrical energy into visible light that can be perceived by the human eye, taking into account the wavelength sensitivity of the eye (see Supplementary Note 2 for details). Dashed lines are guides to the eye, based on a 3rd-order polynomial fit to the data trend. The physical limit for an ideal light source with a colour rendering index of CRI=90, denoted as $K_{max}^{CRI90}$, is shown as a black horizontal line, as per calculations by Murphy et al. \cite{Murphy2012}. The magnified plot shows the progress in cool white LEDs from 1996 to 2020, with the dashed line indicating a linear rate of efficacy improvement of 10lm/W per year. For comparison, efficacies of best performers in legacy lighting technologies for 2020 are shown as coloured horizontal lines. Note the logarithmic scale of the vertical axis on the main plot and the linear scale on the magnified plot. Abbreviations: HID - High-Intensity Discharge; CFL - Compact Fluorescent Lamp; Hal. - Halogen, Incd. - Incandescent. Source: own synthesis of published data based on a visual approach proposed by Azevedo et al. \cite{azevedo2009transition}. See Supplementary Note 16 for the full list of sources and references.}
 \label{fgr:history_efficacy}
 \vspace{-7mm}
\end{figure}

@@

The historical progress in individual sub-efficiencies of warm white phosphor-converted GaN-based LED devices, along with LED innovations and manufacturing process improvements that have driven this progress, is described in Supplementary Note 4. Using this information, we calculate the overall lamp efficiency $\eta_L$ for the best performing mid/high-power phosphor-converted warm white LED devices in four years: 2003, 2010, 2016 and 2020. The waterfall diagrams of electric power input losses in \cref{fgr:waterfall} show how improvements in individual sub-efficiencies led to improvements in the overall white LED lamp efficiency from $\eta_L=5.8\%$ in 2003 to 12.7\% in 2010, 32.5\% in 2016 and finally to 38.8\% in 2020. As is evident from the figure, no single loss channel dominates in terms of its contribution to the overall efficiency, in line with previous observations \cite{tsao2010solid}. We note, however, that the loss channels with a fixed physical limit on efficiency, e.g., Stokes loss that determines the light conversion efficiency by phosphors, became relatively more dominant in 2016 and 2020 compared to 2003 and 2010.  This is a direct result of large efficiency improvements in upstream sub-efficiencies.

>>>>

\newcommand{\hlcolor}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=\textwidth]{figures/history_efficacy.pdf}
 \caption{\textbf{Historical progress in the luminous efficacy ($\eta$) of the most widely-used lighting technologies in human history.} Data points indicate best performers by year of market introduction. Luminous efficacy is the measure of how efficiently a light source converts electrical energy into visible light that can be perceived by the human eye, taking into account the wavelength sensitivity of the eye (see Supplementary Note 2 for details). \hlcolor[green]{Dashed lines are guides to the eye, based on a 3rd-order polynomial fit to the data trend.} The physical limit for an ideal light source with a colour rendering index of CRI=90, denoted as $K_{max}^{CRI90}$, is shown as a black horizontal line, as per calculations by Murphy et al. \cite{Murphy2012}. The magnified plot shows the progress in cool white LEDs from 1996 to 2020, with the dashed line indicating a linear rate of efficacy improvement of 10lm/W per year. For comparison, efficacies of best performers in legacy lighting technologies for 2020 are shown as coloured horizontal lines. Note the logarithmic scale of the vertical axis on the main plot and the linear scale on the magnified plot. Abbreviations: HID - High-Intensity Discharge; CFL - Compact Fluorescent Lamp; Hal. - Halogen, Incd. - Incandescent. Source: own synthesis of published data based on a visual approach proposed by Azevedo et al. \cite{azevedo2009transition}. See Supplementary Note 16 for the full list of sources and references.}
 \label{fgr:history_efficacy}
 \vspace{-7mm}
\end{figure}

@@

\hlcolor[green]{Using the mixed-methods approach described in Methods, we have collected data on the historical progress in individual sub-efficiencies of warm white phosphor-converted GaN-based LED devices, along with white LED innovations that have driven this progress. The results of our data collection efforts are presented in Supplementary Figure 7 and discussed in Supplementary Notes section 4.}Using this information, we calculate the overall lamp efficiency $\eta_L$ for the best performing mid/high-power phosphor-converted warm white LED devices in four years: 2003, 2010, 2016 and 2020. The waterfall diagrams of electric power input losses in \cref{fgr:waterfall} show how improvements in individual sub-efficiencies led to improvements in the overall white LED lamp efficiency from $\eta_L=5.8\%$ in 2003 to 12.7\% in 2010, 32.5\% in 2016 and finally to 38.8\% in 2020. As is evident from the figure, no single loss channel dominates in terms of its contribution to the overall efficiency, in line with previous observations \cite{tsao2010solid}. We note, however, that the loss channels with a fixed physical limit on efficiency, e.g., Stokes loss that determines the light conversion efficiency by phosphors, became relatively more dominant in 2016 and 2020 compared to 2003 and 2010.  This is a direct result of large efficiency improvements in upstream sub-efficiencies.
